An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-29 VLDB2026/main.tex

	Moreover, beyond BigANN, systematic evaluations of hybrid query algorithms remain limited. \textcolor{orange}{Although existing works, such as the surveys in \cite{compare,azizi2025graph}, conduct benchmark evaluations or experimental analyses of ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms. To address this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios. Furthermore, we rigorously assess the robustness of each algorithm under varying conditions, thereby providing valuable insights for future research and practical applications.}

@@

	(1)\textbf{ Systematic Classification and Overview.}
%	We systematically classify 6 representative attribute filtering algorithms along multiple dimensions, including index organization, filtering strategies, Boolean logic support, and index construction methods. In addition, we survey 5 range filtering algorithms, and provide an overview of a vector retrieval library and three vector databases. These efforts offer a unified reference framework for future research.
	\textcolor{orange}{We systematically categorize 6 representative attribute filtering algorithms and 5 range filtering algorithms from the perspectives of index organization, filtering strategies, disk support, and complex attribute handling. We also provide an overview of these algorithms, along with a representative vector retrieval library and 3 vector databases, to help readers intuitively understand their design principles. This work offers a unified reference framework and technical foundation for future research in this field.}

>>>>

	Moreover, beyond BigANN, systematic evaluations of hybrid query algorithms remain limited. \textcolor{orange}{Although existing works \cite{compare,azizi2025graph} conduct benchmark evaluations or experimental analyses of ANN methods, existing work still lacks an experimental study specifically targeting hybrid query algorithms. To address this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios. Furthermore, we rigorously assess the robustness of each algorithm under different experimental settings, thereby providing valuable insights for future research and practical applications.}

@@

	(1)\textbf{ Systematic Classification and Overview.}
%	We systematically classify 6 representative attribute filtering algorithms along multiple dimensions, including index organization, filtering strategies, Boolean logic support, and index construction methods. In addition, we survey 5 range filtering algorithms, and provide an overview of a vector retrieval library and three vector databases. These efforts offer a unified reference framework for future research.
	\textcolor{orange}{We systematically describe the distinct characteristics of 6 representative attribute filtering algorithms and 5 range filtering algorithms from various perspectives. We also provide an overview of these algorithms, along with a representative vector retrieval library and 3 vector databases, to help readers intuitively understand their design principles. This work offers a unified reference framework and technical foundation for future research in this field.}
